Chapter3_ideas

### 2019-12-10 results/Chapter3_ideas99.Rmd
edits, rbar comparisons look more like expected

@@

@@

@@

```{r CO.pos, echo=FALSE}
#male.whole.cell
#female.whole.cell
#fix the data DF for PERMUTING CO

@@

### merge data

```{r merging.data,echo=FALSE}

@@

#
density.plot_rbars <- ggplot(Mus_rbar_male, aes(x = rbar, fill=type) )+geom_density(alpha=.6) + ggtitle("Bivalent Rbar distributions, Mus male")+xlim(c(0,.3))
density.plot_rbars

@@

#
density.plot_cell.wide.rbars <- ggplot(cell.wide.tot.rbar_Musmale, aes(x = sum.rbar, fill=type) )+geom_density(alpha=.6) + ggtitle("Cell wide total Rbar distributions, Mus male")+xlim(c(0,4))

@@

I didn't include the 2 types of simulations? 
rank is not considered for these simluations because -- I assume

I might write in a way to account for rank -- to follow the assumption that the relative foci positions vary for short and long chromosomes. but for now, just simulate across the whole/full pool.

### Map normalized positions onto real SC

```{r map.rand2real, echo=FALSE}

>>>>

For mus, data frames that sample based on SC.length / rank, can be used for SC length and CO count metrics. Not CO position

both SC and CO count randomized data

@@

I think new randomized DFs must be made (male.whole.cell.min, not the DF.list)
(previous ones made lists of DFs, which were made of simulated DFs for each nucleus/cell)
My current code for position data, takes the current real DF, adds new columns with random draws of relative CO positions.

@@

-measure the CO-variation of metrics within cells!
for each cell, make even-rank and odd-rank columns of rbar or another metric. Measure covariance of the 2 sets of pairs (real and random, even-odd).

@@

```{r random.CO.pos, echo=FALSE}
#male.whole.cell
#female.whole.cell
#fix the data DF for PERMUTING CO

@@

### calq within nuc COVARIATION

```{r even.odd, echo=FALSE}
#4 new columns for testing with in nuc covariance

#this doesn't works as well for male 19! (get ride of shortest?)
#make new DF (copy, or empty?)

covary.DF <- male.whole.cell.mini[male.whole.cell.mini$fileName == "1mar16_3jan16_G_m2_sp1_19.3_rev",]
#loop

#I HAVE to make sure they are all ordered by metric, or the pairing for cov() will not make sense

covary.DF <- with(covary.DF, covary.DF[order(SC.length),])
evens <- covary.DF[which(covary.DF$rank %% 2 == 0),]
odds <- covary.DF[which(covary.DF$rank %% 2 != 0),]
cov(evens$SC.length,odds$SC.length[2:10])#303 (lots of variance)
cor(evens$SC.length,odds$SC.length[2:10])# 0.2480786
#do this for each cell / filename

#covary, rbar -- within the same nuc
#real and rand cov
for(y in 1:length(covary.DF$fileName)  ){
  covary.DF$rbar[y] <- calq.intra.rbar(covary.DF[y,])
}

covary.DF <- with(covary.DF, covary.DF[order(rbar),])
evens <- covary.DF[which(covary.DF$rank %% 2 == 0),]
odds <- covary.DF[which(covary.DF$rank %% 2 != 0),]

cov(evens$rbar,odds$rbar[2:10])#0.007357481
cor(evens$rbar,odds$rbar[2:10])# 0.9734986
#I don't know how to interpert the scales of the covariaition values...
#correlation is simpler to me

#male.whole.cell.mini
#counter of file

for(y in 1:length(male.whole.cell.mini$fileName)  ){
  male.whole.cell.mini$rbar[y] <- calq.intra.rbar(male.whole.cell.mini[y,])
}
for(rr in 1:length(male.whole.cell.mini$fileName)  ){
  male.whole.cell.mini$rand.rbar[rr] <- calq.intra.rbar_rand(male.whole.cell.mini[rr,])
}

#make smaller cell.level DF
smllr.list = data.frame(fileName = unique(male.whole.cell.mini$fileName))
i = 1
#the loop isn't cycling
for(each in unique(male.whole.cell.mini$fileName) ) {
 # print(each)

  #make smaller DF, list of all obs of that file
  temp.Df = male.whole.cell.mini[ male.whole.cell.mini$fileName == each,]
  ordered.DF.rbar = with(temp.Df, temp.Df[order(rbar),])

  #order by the metric (SC,rbar)  #make list of even and odd
  evens <- ordered.DF.rbar$rbar[which(ordered.DF.rbar$rank %% 2 == 0)]
  odds <- ordered.DF.rbar$rbar[which(ordered.DF.rbar$rank %% 2 != 0)]

  evens.rand <- ordered.DF.rbar$rand.rbar[which(ordered.DF.rbar$rank %% 2 == 0)]
  odds.rand <- ordered.DF.rbar$rand.rbar[which(ordered.DF.rbar$rank %% 2 != 0)]

  #calq cor,cov
  smllr.list$fileName[i] <- each
  smllr.list$cov[i] <- cov(evens,odds[2:10])
  smllr.list$cor[i] <- cor(evens,odds[2:10])

  smllr.list$cov.rand[i] <- cov(evens.rand, odds.rand[2:10])
  smllr.list$cor.rand[i] <- cor(evens.rand, odds.rand[2:10])

  #print(i)
  i = i+1
  }

#plotty <- ggplot(smllr.list, #aes(x=cov,y=cov.rand))+geom_jitter()+xlim(c(-.005,.006))+ylim(c(-.005,.006))

Calq the within cell covariance for the true and randomized values. 
Not sure how to use them yet

### merge melt data

don't use melt data

```{r melt.data,echo=FALSE}

@@

dense1 <- ggplot(real_rbar.Mus, aes(x = rbar, fill=type) )+geom_density(alpha=.6)

#
density.plot_rbars <- ggplot(Mus_rbar_male, aes(x = rbar, fill=type) )+geom_density(alpha=.6) + ggtitle("Bivalent Rbar distributions, Mus male")+xlim(c(0,.55))
density.plot_rbars

@@

#
density.plot_cell.wide.rbars <- ggplot(cell.wide.tot.rbar_Musmale, aes(x = sum.rbar, fill=type) )+geom_density(alpha=.6) + ggtitle("Cell wide total Rbar distributions, Mus male")+xlim(c(0,6))

@@

I might write in a way to account for rank, to account for how the relative foci positions vary for short and long chromosomes. but for now, just simulate across the whole/full pool.

```{r map.rand2real, echo=FALSE, warning=FALSE}
